\documentclass[journal]{IEEEtai}

\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,citecolor=blue]{hyperref}

\usepackage{color,array}

\usepackage{graphicx}

%% change the following later - leftover from template
%% \jvol{XX}
%% \jnum{XX}
%% \paper{1234567}
%% \pubyear{2020}
%% \publisheddate{xxxx 00, 0000}
%% \currentdate{xxxx 00, 0000}
%% \doiinfo{TQE.2020.Doi Number}


\setcounter{page}{1}
%% \setcounter{secnumdepth}{0}


\begin{document}


\title{Style in the Weights: Age-Adaptive LoRA Adapters Without System Prompts for Pediatric VR} 


\author{authors go here}

\maketitle

\begin{abstract}
The abstract should not exceed 250 words. This example is 250 words. See instructions give you guidelines for preparing papers for IEEE Transactions and Journals. Use this document as a template if you are using Microsoft {\bi Word} 6.0 or later. Otherwise, use this document as an instruction set. The electronic file of your paper will be formatted further at IEEE. Paper titles should be written in uppercase and lowercase letters, not all uppercase. Avoid writing long formulas with subscripts in the title; short formulas that identify the elements are fine (e.g., ``Nd--Fe--B''). Do not write ``(Invited)'' in the title. Full names of authors are preferred in the author field, but are not required. Put a space between authors' initials. The abstract must be a concise yet comprehensive reflection of what is in your article. In particular, the abstract must be self-contained, without abbreviations, footnotes, or references. It should be a microcosm of the full article. The abstract must be between 150--250 words. Be sure that you adhere to these limits; otherwise, you will need to edit your abstract accordingly. The abstract must be written as one paragraph, and should not contain displayed mathematical equations or tabular material. The abstract should include three or four different keywords or phrases, as this will help readers to find it. It is important to avoid over-repetition of such phrases as this can result in a page being rejected by search engines. Ensure that your abstract reads well and is grammatically correct.
\end{abstract}

\section{Introduction}

\IEEEPARstart{T}{his} document is a template... (intro here). Gotta get to 6 pages with the double column

\section{Related Work}
a
\subsection{Subsection}
a2
\subsection{Subsection}
a3
\section{Dataset}
dataset here - will likely need tables for this and results so look into that (or use the pngs from the presentation)

\section{Methodlogy}
Methodlogy here

\section{Results}
results here

\section{Discussion/Conclusion}
Conclusion

\section*{Appendix}

Appendixes, if needed, appear before the acknowledgment. (there will be many)

\subsection{Repository Link}
goes here

\subsection{Group Member Contributions}
goes here

\subsection{Claude Transcripts}
(specify claude version here too?)

\section*{References and Footnotes}

References go here - see template for potential Latex code needed?

\end{document}
